The evolution of gene expression in the term placenta of viviparous mammals

### 2016-08-12 manuscript/manuscript.Rnw
use mtime instead of md5sum

<<source.to.latex,echo=FALSE,message=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../common_r_code/",c("to_latex.R","plot_tree_matrix.R","utility_functions.R")))>>=
for (a in paste0("../common_r_code/",c("to_latex.R","plot_tree_matrix.R","utility_functions.R"))) {
    source(a)
}
@

<<load.data,echo=FALSE,results="hide",cache.extra=tools::md5sum(paste0("../data/",c("combined_fpkm","gene_trees","housekeeping_genes_superset","placenta_core_transcriptome","placenta_go_results_bp","placenta_go_results_mf","hugo_nomenclature","gene_annotation")))>>=
for (a in paste0("../data/",c("combined_fpkm","gene_trees",
                              "housekeeping_genes_superset",
                              "placenta_core_transcriptome",
                              "placenta_go_results_bp",
                              "placenta_go_results_mf",
                              "hugo_nomenclature",
                              "gene_annotation"
                              ))) {
    load(a)
}
combined.fpkm[,species:=factor(species,levels=names(species.names))]
setkey(genes.to.tree,"gene_id")
star.logs[,value:=gsub("%$","",value)]
star.logs.wide <- 
    data.table(dcast(star.logs,species+file~field))
setnames(star.logs.wide,
         "Average input read length",
         "input.read.length")
setnames(star.logs.wide,
         "Number of input reads",
         "input.reads")
setnames(star.logs.wide,
         "Uniquely mapped reads number",
         "unique.map.reads")
star.logs.wide[,`% bad reads`:=(as.numeric(`% of reads mapped to too many loci`)+
                            as.numeric(`% of reads unmapped: other`)+
                            as.numeric(`% of reads unmapped: too many mismatches`)+
                            as.numeric(`% of reads unmapped: too short`))]
star.logs.wide[,`% good reads`:=100-`% bad reads`]
star.logs.wide[,input.reads:=as.numeric(input.reads)]
star.logs.wide[,input.read.length:=as.numeric(input.read.length)]
setkey(hugo.nomenclature,"Approved Symbol")
@

>>>>

<<source.to.latex,echo=FALSE,message=FALSE,results="hide",cache.extra=file.info(paste0("../common_r_code/",c("to_latex.R","plot_tree_matrix.R","utility_functions.R")))[,"mtime"]>>=
for (a in paste0("../common_r_code/",c("to_latex.R","plot_tree_matrix.R","utility_functions.R"))) {
    source(a)
}
@

<<load.data,echo=FALSE,results="hide",cache.extra=file.info(paste0("../data/",c("combined_fpkm","gene_trees","housekeeping_genes_superset","placenta_core_transcriptome","placenta_go_results_bp","placenta_go_results_mf","hugo_nomenclature","gene_annotation")))[,"mtime"]>>=
for (a in paste0("../data/",c("combined_fpkm","gene_trees",
                              "housekeeping_genes_superset",
                              "placenta_core_transcriptome",
                              "placenta_go_results_bp",
                              "placenta_go_results_mf",
                              "hugo_nomenclature",
                              "gene_annotation"
                              ))) {
    load(a)
}
combined.fpkm[,species:=factor(species,levels=names(species.names))]
setkey(genes.to.tree,"gene_id")
star.logs[,value:=gsub("%$","",value)]
star.logs.wide <- 
    data.table(dcast(star.logs,species+file~field))
setnames(star.logs.wide,
         "Average input read length",
         "input.read.length")
setnames(star.logs.wide,
         "Number of input reads",
         "input.reads")
setnames(star.logs.wide,
         "Uniquely mapped reads number",
         "unique.map.reads")
star.logs.wide[,`% bad reads`:=(as.numeric(`% of reads mapped to too many loci`)+
                            as.numeric(`% of reads unmapped: other`)+
                            as.numeric(`% of reads unmapped: too many mismatches`)+
                            as.numeric(`% of reads unmapped: too short`))]
star.logs.wide[,`% good reads`:=100-`% bad reads`]
star.logs.wide[,input.reads:=as.numeric(input.reads)]
star.logs.wide[,input.read.length:=as.numeric(input.read.length)]
setkey(hugo.nomenclature,"Approved Symbol")
@
